### 2024-02-21 documentation/thesis/thesis_document.tex
.

To address this challenge, the thesis proposes the development of a
comprehensive hardware and software framework. The hardware system aims
to selectively measure magnetic fields at various locations or fully
around a permanent magnet using different sensors. Several existing
open-source software solutions implement individual parts, but do not
provide a complete data processing pipeline from acquisition to
analysis, and their data storage formats are not compatible with each
other. The accompanying open source software for this work is not only
designed to enable measurements with various sensors, but also to
characterise permanent magnets, magnetic fields and the sensors
themselves.

@@

For modern medical imaging high-field superconducting magnets dominate
most \gls{mri} machines, providing high black-withe image resolution.
However, the substantial costs, space requirements and safety
considerations cause considerable challenges.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Example_Halbach_ring_with_cutouts_for_eight_magnets.png}
\caption{Example Halbach ring with cutouts for eight magnets
\label{Example_Halbach_ring_with_cutouts_for_eight_magnets.png}}
\end{figure}

@@

A Halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The figure
\ref{Example_Halbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring.

@@

\begin{itemize}
\item
  \textbf{Material}: The magnetic properties of a material influence the
  generated field strength. Various materials have different magnetic
  susceptibilities.
\item
  \textbf{Magnetization}: The orientation of the magnetic moments in the
  material influences the field strength. A higher magnetization leads
  to a stronger field strength.
\item
  \textbf{Temperature}: Temperature can influence the magnetic
  properties of a material. The magnetization of some materials
  decreases with increasing temperature.
\item
  \textbf{Manufacturing process}: The manufacturing process can
  influence the magnetic properties of the material. This is dependent
  on the purity of the starting materials used and the processing
  methods. There may also be deviations in field strength if different
  magnets from different production batches are compared.
  \customcite{BC16}
\end{itemize}

These aspects can also be applied to individual magnets. As a result,
this also complicates the effect on the structure of a Halbach ring
magnet. If these are joined together to form a ring, positioning
tolerances are also added.

@@

According to Wolfgang R. Nitz in 2016, just \emph{13.4\%} of actively
used \gls{mri} systems are low-field \gls{mri} (\emph{66.6\% 1.5T
systems, 20\% 3.0 T system, 14.4\% low field with \textless0.5T}).
\customcite{NK16}

@@

The shimming process described describes how, after the field magnet has
been set up, if the homogeneous magnetic flux densities are not
sufficient, these can be adjusted manually by means of adjustments to
the setup or, if the hardware allows it, by software. In addition, the
causes that cause the inhomogeneity, the output permanent magnet, are
also known. As a result, there is the possibility of using the shimming
process or checking the permanent magnets used in advance before they
are used in a Halbach configuration.

@@

Beyond the development and prototype construction of low-field \gls{mri}
scanners, the project encompasses electromagnetic simulation of
components within the low-field \gls{mri} system, coupled with machine
learning-driven control and data acquisition. The resultant software
will be instrumental in reconstruction, with a specific focus on
leveraging AI-based methodologies.

This comprehensive effort serves to bolster the prototyping phase of the
low-field \gls{mri}. Diverging from the approach implemented by
O'Reilly, Teeuwisse, and Webb, \emph{DeLoRI} aims to design an open
\gls{mri}, departing from the circular \gls{mri} configuration discussed
in the publication. This innovation is geared towards streamlining
breast examinations, offering enhanced accessibility, and minimizing the
spatial requirements during installation.

In addition, \emph{DeLoRI} efforts to achieve heightened accuracy,
striving for precision levels below \emph{1000 \gls{ppm}}. While
O'Reilly, Teeuwisse, and Webb were able to modify the ring diameter to
influence field homogeneity, the unique goal at this point is to
characterize the magnets pre-installation, allowing for proactive
assessments of homogeneity characteristics. This approach aims to
provide insights into magnetic field uniformity before the magnets are
integrated, thereby streamlining the optimisation process. Furthermore,

It is important to note that the primary objective of this thesis is not
merely to characterize the magnet itself; rather, the emphasis lies in
the selection and comparison of potential sensors for the
characterisation process. To achieve this, a versatile hardware setup is
in development, designed to accommodate various sensors for the
measurement of magnets or other objects. Simultaneously, a software
interface is being crafted to universally read data from different
sensors and interact seamlessly with the diverse firmware associated
with various Halbach sensors. A key feature of this system is the ease
of sensor interchangeability, facilitating adaptability and versatility
in the characterisation process.

@@

\noteworthy{\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT }{: 1000ppm from 50mT needed resolution calucation I}

To convert this into microtesla (\(\mu\)T), a multiplication by
\emph{1000} is needed:

\noteworthy{0.05 \, mT \times 1000 = 50 \, \mu T}{: 1000ppm from 50mT needed resolution calucation II}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}
\caption{Typical block diagram of a digital hall sensor sensing chain
using three hall plates
\label{Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}}
\end{figure}

@@

The figure
\ref{Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}
shows the internal structure of a digital Hall effect sensor as a block
diagram. The Hall effect takes place in the Hall plates. These are
orientated differently depending on the axis inside the \gls{ic}s. In
this case, it is a three-axis hall effect sensor. The output voltage
generated by the Hall plates is then digitised by a \gls{adc}. The
values can then be read out via a digital interface.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{List of in unified firmware implemented digital magnetic field
sensors with focus on different sensor capabilities
\label{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}}\tabularnewline
\toprule
& TLV493D & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endfirsthead
\toprule
& TLV493D & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endhead
Readout-Axis & 3D & 3D & 3D & 1D\tabularnewline
Temperature-Sensor & yes & no & yes & no\tabularnewline
Resolution {[}uT{]} & 98 & 0.2 & 0.007 & 48\tabularnewline
Range {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
Interface & \gls{i2c} & \gls{i2c} & \gls{i2c} & \gls{i2c}\tabularnewline
\bottomrule
\end{longtable}

@@

Another point that contributed to the selection of this module is the
availability of the sensor \gls{ic}s as a ready-made and readily
available evaluation module. This ensured that the electrical design is
verified by the manufacturer so that the sensor could be operated with
the correct electrical parameters. On the other hand, it is possible to
evaluate several sensors in a shorter time, as a separate \gls{pcb} has
to be produced here.

The table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
shows a selection of sensors for which hardware and software support has
been implemented. The resolution of the selected sensors covers the
expected range of values required by the various magnets to be tested.

In the \emph{Evaluation} in chapter \ref{evaluation} basic
characterisation methods are used to evaluate the sensors listed in
table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
regarding their sensitivity and other parameters. This is done at this
point, as the components of the readout interface that enable
interaction with the sensors are considered first.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png}
\caption{Rendered mechanical structure of the 1D sensor \gls{cad} model
with different parts colored separately, and universal magnet mount
shown in green
\label{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png}}
\end{figure}

Figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png},
shows rendered view of the 1D-Single sensor \gls{cad} drawing, which is
described in chapter \ref{d-single-sensor}. All parts are produced using
3D printing additive manufacturing process. The sensor circuit board is
glued underneath the magnet holder. This is interchangeable, so
different distances between sensor and magnet can be realised. The
exchangeable magnetic holder (shown in green in figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
can be adapted to different magnets. It can be produced quickly due to
the small number of parts used. The two recesses lock the magnet holder
with the inserted magnet over the sensor. The specified tolerances allow
the magnet to be inserted into the holder with repeat accuracy and
without backlash. This is important if several magnets must be measured,
where the positioning over the sensor must always be the same.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}
\caption{1D sensor schematic using an Raspberry Pi Pico with a TLV493D
footprint in the center
\label{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}}
\end{figure}

@@

All the necessary components and their circuitry are recorded on a
\gls{pcb} shown in figure
\ref{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}
and subsequently manufactured. In addition, footprints are provided for
various sensor \gls{ic} packages. By placing mounting holes on the
\gls{pcb}, it is possible to attach various mechanical mounts on top of
the sensor \gls{ic}s. These holes are necessary for later adaptions and
sensor changes, such as different magnet holders or measurement
equipment (e.g.~for additional temperature sensors).

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}
\caption{Unified sensor firmware program structure with listed setup and
main loop routines using simplified function blocks
\label{Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}}
\end{figure}

The microcontroller firmware is software that is executed on a
microcontroller in an embedded system. It controls the hardware and
enables the execution of predefined functions. The firmware is used to
process input data, control output devices and performs specific tasks
according to the program code. It manages communication with sensors,
actuators and other peripheral devices, processing data and making
decisions. Firmware is critical to the functioning of devices. The
firmware is responsible for detecting the possible connected sensors
shown in table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
and query measurements. This measured data can be forwarded to a host
\gls{pc} via a user interface and can then be further processed there.

A key component is that as many common sensors as possible can be easily
connected without having to adapt the firmware. This modularity is
implemented using abstract class design. These are initiated according
to the sensors found at startup. If new hardware needs to be integrated,
only the required functions in listing \ref{lst:CustomSensorClass} need
to be implemented.

@@

The figure
\ref{Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}
shows a flow chart of the start process after powering on the sensor and
the subsequent main loop for processing the user commands and sensor
results. When the microcontroller is started, the software checks
whether known sensors are connected to \gls{i2c} or \gls{uart}
interfaces.

@@

This ensures that in a multi-sensor setup with several sensors. The
measurements are synchronized in time like described in chapter
\ref{sensor-synchronisation-interface} and are not out of sequence or
drift.

@@

\begin{itemize}
\tightlist
\item
  Use with \gls{mrp}-library, explained in chapter
  \ref{software-readout-framework}
\item
  Stand-alone mode via sending commands using built-in \gls{cli}
\end{itemize}

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly inspect whether the
hardware is working properly after firmware installation. The command
\emph{help}, displays a detailed command reference with all available
commands as shown in the figure
\ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
to the user.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
\caption{Unified sensor firmware provided serial terminal based
\gls{cli} allows the user to configure the sensor manually
\label{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}}
\end{figure}

The figure
\ref{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
shows the current measured value queried by using the \emph{readout}
command by the user.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
\caption{Result of an executed b value measurement readout command using
the sensors \gls{cli} with immediate user readable response
\label{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
\caption{Multi sensor synchronisation wiring example using three sensors
together with one host \gls{pc} performing the triggering and readout
processing
\label{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}}
\end{figure}

@@

A jitter time of up to an additional \emph{1ms} is added between the
triggering of the measurements by the host system and the receipt of the
command by the sensor hardware. If the host system is still under load,
this value increases many times over. This means that synchronising
several sensors via the \gls{usb} connection alone is not sufficient.
The other issue is sending the trigger signal from the readout software,
which is described in chapter \ref{software-readout-framework}. At this
point unpredictable latencies can occur, too, depending on which other
tasks are also executed on this port. To enable the most stable possible
synchronisation between several sensors, an option has already been
created to establish an electrical connection between sensors. This is
used together with the firmware to synchronise the readout intervals.
The figure
\ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
illustrates the schematic how several sensors must be wired together to
implement this form of synchronisation.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
\caption{Unified sensor firmware multi sensor synchronisation procedure
using sync \gls{gpio} input for operation (primary or secondary) mode
decision
\label{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}}
\end{figure}

Once the hardware has been prepared, the task of the firmware of each of
the chained sensors is to find a common synchronisation clock. The
figure
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
illustrates how the firmware handles the decision task if the sensor is
\emph{primary} or \emph{secondary} at startup. The internal
firmware-function \emph{register irq on sync pin} is overwritten. To set
one \emph{primary} and several \emph{secondary} sensors, each sensor
waits for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
microcontroller with the functionality to detect if the sensor is a
primary or a secondary sensor. A random timer is started beforehand by
each sensor, which sends a pulse on the sync line. All others receive
this and switch to \emph{secondary mode} and synchronise the
measurements based on each sync pulse received.

@@

In single-sensor operation, this automatically jumps to \emph{primary}
sensor operation through the \emph{got impulse within 1000ms} branch
result. The figure
\ref{Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}
shows the synchronisation status of the sensor which can be queried via
the user interface described in chapter \ref{communication-interface} by
using the \emph{opmode} command. An important aspect of the
implementation is that there is no numbering or sequence of the
individual sensors. This means that for the subsequent readout of the
measurements, it is only important that they are taken at the same
interval across all sensors. The sensor differentiation takes place
later in the \gls{mrp}-library \ref{software-readout-framework} by using
the sensor \gls{uuid}.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}
\caption{Result of the opmode command execution on a sensor which is
connected to another as primary configured sensor
\label{Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}}
\end{figure}

@@

In order to be able to read and correctly interpret the data from the
microcontroller, the serial protocol of the sensor is implemented in a
customised version of the \emph{CustomSensor} class as shown in listing
\ref{lst:CustomSensorClass}. This software or hardware integration can
be conducted on any other measuring device with a suitable communication
interface and a known protocol thanks to the modular design.

>>>>

To address this challenge, the thesis proposes the development of a
comprehensive hardware and software framework. The hardware system aims
to selectively measure magnetic fields at various locations or fully
around a permanent magnet using different sensors. Several existing
open-source software solutions implement individual parts, but do not
provide a complete data processing pipeline from acquisition to
analysis, and their data storage formats are not compatible with each
other. These projects and their incompatibilities are explained in
detail in chapter \ref{user-interaction-points-example}.

The accompanying open source software for this work is not only designed
to enable measurements with various sensors, but also to characterise
permanent magnets, magnetic fields and the sensors themselves.

@@

For modern medical imaging high-field superconducting magnets dominate
most \gls{mri} machines, providing in general a higher image contrast.
The substantial costs, space requirements and safety and installation
considerations cause considerable challenges.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Example_Halbach_ring_with_cutouts_for_eight_magnets.png}
\caption{Example Halbach ring with cutouts for eight magnets.
\label{Example_Halbach_ring_with_cutouts_for_eight_magnets.png}}
\end{figure}

@@

A Halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The Figure
\ref{Example_Halbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring.

@@

\begin{itemize}
\item
  \textbf{Material}: The magnetic properties of a material influence the
  generated field strength. Various materials have different magnetic
  susceptibilities.
\item
  \textbf{Magnetization}: The orientation of the magnetic moments in the
  material influences the field strength. A higher magnetization leads
  to a stronger field strength.
\item
  \textbf{Temperature}: Temperature can influence the magnetic
  properties of a material. The magnetization of some materials
  decreases with increasing temperature.
\item
  \textbf{Manufacturing process}: The manufacturing process can
  influence the magnetic properties of the material. This is dependent
  on the purity of the starting materials used and the processing
  methods. There may also be deviations in field strength if different
  magnets from different production batches are compared.
\end{itemize}

These aspects \customcite{BC16} can also be applied to individual magnets.
As a result, this also complicates the effect on the structure of a
Halbach ring magnet. If these are joined together to form a ring,
positioning tolerances are also added.

@@

According to Wolfgang R. Nitz in 2016, just \emph{13.4\%} of actively
used \gls{mri} systems are low-field \gls{mri} (\emph{66.6\% 1.5T
systems, 20\% 3.0T system, 14.4\% low field with \textless0.5T}).
\customcite{NK16}

@@

The shimming process mentioned describes how, after the field magnet has
been set up, if the homogeneous magnetic flux densities are not
sufficient, these can be adjusted manually by means of adjustments to
the setup or, if the hardware allows it, by software. In addition, the
causes that cause the inhomogeneity, the output permanent magnet, are
also known. As a result, there is the possibility of using the shimming
process or checking the permanent magnets used in advance before they
are used in a Halbach configuration.

@@

Beyond the development and prototype construction of low-field \gls{mri}
scanners, the project encompasses electromagnetic simulation of
components within the low-field \gls{mri} system, coupled with machine
learning-driven control and data acquisition. The resultant software
will be instrumental in reconstruction, with a specific focus on
leveraging \gls{ai}-based methodologies.

This comprehensive effort is designed to support the prototyping phase
of the low-field \gls{mri}. Diverging from the approach implemented by
O'Reilly, Teeuwisse, and Webb, \emph{DeLoRI} aims to design an open
\gls{mri}, departing from the circular \gls{mri} configuration discussed
in the publication. This innovation is geared towards streamlining
breast examinations, offering enhanced accessibility, and minimizing the
spatial requirements during installation.

In addition, \emph{DeLoRI} efforts to achieve heightened accuracy,
striving for precision levels below \emph{1000 \gls{ppm}}. While
O'Reilly, Teeuwisse, and Webb were able to modify the ring diameter to
influence field homogeneity, the unique goal at this point is to
characterize the magnets pre-installation, allowing for proactive
assessments of homogeneity characteristics. This approach aims to
provide insights into magnetic field uniformity before the magnets are
integrated, thereby streamlining the optimisation process. Furthermore,
it is important to note that the primary objective of this thesis is not
merely to characterize the magnet itself; rather, the emphasis lies in
the selection and comparison of potential sensors for the
characterisation process. To achieve this, a versatile hardware setup is
in development, designed to accommodate various sensors for the
measurement of magnets or other objects. Simultaneously, a software
interface is being crafted to universally read data from different
sensors and interact seamlessly with the diverse firmware associated
with various Halbach sensors. A key feature of this system is the ease
of sensor interchangeability, facilitating adaptability and versatility
in the characterisation process.

@@

\noteworthy{\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT \times 1000 = 50 \, \mu T}{: 1000ppm from 50mT needed resolution calucation I}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}
\caption{Typical block diagram of a digital hall sensor sensing chain
using three hall plates.
\label{Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}}
\end{figure}

@@

The Figure
\ref{Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}
shows the internal structure of a digital Hall effect sensor as a block
diagram. The Hall effect takes place in the Hall plates. These are
orientated differently depending on the axis inside the \gls{ic}s. In
this case, it is a three-axis hall effect sensor. The output voltage
generated by the Hall plates is then digitised by a \gls{adc}. The
values can then be read out via a digital interface.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{List of in unified firmware implemented digital magnetic field
sensors with focus on different sensor capabilities.
\label{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}}\tabularnewline
\toprule
& TLV493D & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endfirsthead
\toprule
& TLV493D & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endhead
Readout-Axis & 3D & 3D & 3D & 1D\tabularnewline
Temperature-Sensor & yes & no & yes & no\tabularnewline
Resolution {[}uT{]} & 98 & 0.2 & 0.007 & 48\tabularnewline
Range {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
Interface & \gls{i2c} & \gls{i2c} & \gls{i2c} & \gls{i2c}\tabularnewline
\bottomrule
\end{longtable}

@@

Another point that contributed to the selection of this module is the
availability of the sensor \gls{ic}s as a ready-made and readily
available evaluation module. This ensured that the electrical design is
verified by the manufacturer so that the sensor could be operated with
the correct electrical parameters. On the other hand, it is possible to
analyse several sensors in a shorter time, so that no separate \gls{pcb}
has to be designed and manufactured.

The Table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
shows a selection of sensors for which hardware and software support has
been implemented. The resolution of the selected sensors covers the
expected range of values required by the various magnets to be tested.

In the \emph{Evaluation} in chapter \ref{evaluation} basic
characterisation methods are used to evaluate the sensors listed in
Table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
regarding their sensitivity and other parameters. This is done at this
point, as the components of the readout interface that enable
interaction with the sensors are considered first.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png}
\caption{Rendered mechanical structure of the 1D sensor \gls{cad} model
with different parts colored separately, and universal magnet mount
shown in green.
\label{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png}}
\end{figure}

Figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png},
shows rendered view of the 1D-Single sensor \gls{cad} drawing, which is
described in chapter \ref{d-single-sensor}. All parts are produced using
3D printing additive manufacturing process. The sensor circuit board is
glued underneath the magnet holder. This is interchangeable, so
different distances between sensor and magnet can be realised. The
exchangeable magnetic holder (shown in green in Figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
can be adapted to different magnets. It can be produced quickly due to
the small number of parts used. The two recesses lock the magnet holder
with the inserted magnet over the sensor. The specified tolerances allow
the magnet to be inserted into the holder with repeat accuracy and
without backlash. This is important if several magnets must be measured,
where the positioning over the sensor must always be the same.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}
\caption{1D sensor schematic using an Raspberry Pi Pico with a TLV493D
footprint in the center.
\label{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}}
\end{figure}

@@

All the necessary components and their circuitry are recorded on a
\gls{pcb} shown in Figure
\ref{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}
and subsequently manufactured. In addition, footprints are provided for
various sensor \gls{ic} packages. By placing mounting holes on the
\gls{pcb}, it is possible to attach various mechanical mounts on top of
the sensor \gls{ic}s. These holes are necessary for later adaptions and
sensor changes, such as different magnet holders or measurement
equipment (e.g.~for additional temperature sensors).

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}
\caption{Unified sensor firmware program structure with listed setup and
main loop routines using simplified function blocks.
\label{Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}}
\end{figure}

The microcontroller firmware is software that is executed on a
microcontroller in an embedded system. It controls the hardware and
enables the execution of predefined functions. The firmware is used to
process input data, control output devices and performs specific tasks
according to the program code. It manages communication with sensors,
actuators and other peripheral devices, processing data and making
decisions. Firmware is critical to the functioning of devices. The
firmware is responsible for detecting the possible connected sensors
shown in Table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
and query measurements. This measured data can be forwarded to a host
\gls{pc} via a user interface and can then be further processed there.

A key component is that as many common sensors as possible can be easily
connected without having to adapt the firmware. This modularity is
implemented using abstract class design. These are initiated according
to the sensors found at startup. If new hardware needs to be integrated,
only the required functions in Listing \ref{lst:CustomSensorClass} need
to be implemented.

@@

The Figure
\ref{Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}
shows a flow chart of the start process after powering on the sensor and
the subsequent main loop for processing the user commands and sensor
results. When the microcontroller is started, the software checks
whether known sensors are connected to \gls{i2c} or \gls{uart}
interfaces.

@@

This ensures that in a multi-sensor setup with several sensors are
synchronized in time like described in chapter
\ref{sensor-synchronisation-interface} and are not out of sequence or
drift.

@@

\begin{itemize}
\tightlist
\item
  \gls{mrp}-library, explained in chapter
  \ref{software-readout-framework}
\item
  Stand-alone mode via sending commands using built-in \gls{cli}
\end{itemize}

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly inspect whether the
hardware is working properly after firmware installation. The command
\emph{help}, displays a detailed command reference with all available
commands as shown in the Figure
\ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
to the user.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
\caption{Unified sensor firmware provided serial terminal based
\gls{cli} allows the user to configure the sensor manually.
\label{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}}
\end{figure}

The Figure
\ref{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
shows the current measured value queried by using the \emph{readout}
command by the user.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
\caption{Result of an executed b value measurement readout command using
the sensors \gls{cli} with immediate user readable response.
\label{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
\caption{Multi sensor synchronisation wiring example using three sensors
together with one host \gls{pc} performing the triggering and readout
processing.
\label{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}}
\end{figure}

@@

A jitter time of up to an additional \emph{1ms} is added between the
triggering of the measurements by the host system and the receipt of the
command by the sensor hardware. If the host system is still under load,
this value increases many times over. This means that synchronising
several sensors via the \gls{usb} connection alone is not sufficient.
The other issue is sending the trigger signal from the readout software,
which is described in chapter \ref{software-readout-framework}. At this
point unpredictable latencies can occur, too, depending on which other
tasks are also executed on this port. To enable the most stable possible
synchronisation between several sensors, an option has already been
created to establish an electrical connection between sensors. This is
used together with the firmware to synchronise the readout intervals.
The Figure
\ref{Multi_sensor_synchronisation_wiring_example_using_three_sensors_together_with_one_host_(+pc)_performing_the_triggering_and_readout_processing.png}
illustrates the schematic how several sensors must be wired together to
implement this form of synchronisation.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
\caption{Unified sensor firmware multi sensor synchronisation procedure
using sync \gls{gpio} input for operation (primary or secondary) mode
decision.
\label{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}}
\end{figure}

Once the hardware has been prepared, the task of the firmware of each of
the chained sensors is to find a common synchronisation clock. The
Figure
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
illustrates how the firmware handles the decision task if the sensor is
\emph{primary} or \emph{secondary} at startup. The internal
firmware-function \emph{register irq on sync pin} is overwritten. To set
one \emph{primary} and several \emph{secondary} sensors, each sensor
waits for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
microcontroller with the functionality to detect if the sensor is a
primary or a secondary sensor. A random timer is started beforehand by
each sensor, which sends a pulse on the sync line. All others receive
this and switch to \emph{secondary mode} and synchronise the
measurements based on each sync pulse received.

@@

In single-sensor operation, this automatically jumps to \emph{primary}
sensor operation through the \emph{got impulse within 1000ms} branch
result. The Figure
\ref{Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}
shows the synchronisation status of the sensor which can be queried via
the user interface described in chapter \ref{communication-interface} by
using the \emph{opmode} command. An important aspect of the
implementation is that there is no numbering or sequence of the
individual sensors. This means that for the subsequent readout of the
measurements, it is only important that they are taken at the same
interval across all sensors. The sensor differentiation takes place
later in the \gls{mrp}-library \ref{software-readout-framework} by using
the sensor \gls{uuid}.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}
\caption{Result of the opmode command execution on a sensor which is
connected to another as primary configured sensor.
\label{Result_of_the_opmode_command_execution_on_a_sensor_which_is_connected_to_another_as_primary_configured_sensor.png}}
\end{figure}

@@

In order to be able to read and correctly interpret the data from the
microcontroller, the serial protocol of the sensor is implemented in a
customised version of the \emph{CustomSensor} class as shown in Listing
\ref{lst:CustomSensorClass}. This software or hardware integration can
be conducted on any other measuring device with a suitable communication
interface and a known protocol thanks to the modular design.
